The Ultraviolet Radiation Environment of a Tropical Megacity in Transition: Mexico City 2000-2019

### 2021-07-07 Paper_third_version/Article_UV_Mexico.tex
Change table  4 and add figure 8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{chemformula} % Formula subscripts using \ch{}
\usepackage[T1]{fontenc} % Use modern font encodings
\usepackage{lineno}
\usepackage{achemso}
\setkeys{acs}{maxauthors=20}
\setkeys{acs}{etalmode=truncate}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{multirow}

@@

The question of how air pollution alters the urban UV environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
with relatively few available observations (e.g.,
\citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
reviewed by \citet{Bais_2015}). Increases in UV have been estimated as a consequence
of emission reductions over the last decades, e.g. in China,\citep{Hollaway_2019,Li_2018,Wang_2020}
and have led to less-than-expected
reductions in photochemical smog, in part due to stronger UV
photochemistry.\citep{Wang_2019,Gao_2020,Ma_2021}
Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\citep{Bauwens_2020,Venter_2020}
but ground-level ozone in some polluted areas has actually
increased,\citep{Shi_2020,Le_2020} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-derived
hypotheses.~~

@@

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized metric of UV
radiation\citep{who2002} for global public information. An advantage
of using the UVI as (one) measure of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons among seasons and locations. The UVI observations
from Mexico City, considered here, are an important element of this
global picture.

@@

The UV Index data derived from satellite-based measurements
were used for comparing to the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated in cooperation between the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths. The ozone column is estimated by differential absorption of several adjacent wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006} while clouds are estimated from the reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm, \citet{Tanskanen_2007}). A correction for absorbing aerosols is made using a global aerosol climatology\citep{Arola_2009}.
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

Above the atmospheric boundary layer, the model atmosphere was specified to be,
NO\textsubscript{2}, or SO\textsubscript{2}. In one
sensitivity study, a total AOD of 0.7 was redistributed placing 0.2 in
the free troposphere (decreasing vertically with an exponential scale
height of 4 km, and 0.5 remaining in the BL). The calculated UVI
differed by less than 1\%. Thus, as long as the total AOD is known,
knowledge of the exact vertical aerosol profile is not critical for
ground-level UVI but would obviously affect the vertical structure of
photolysis frequencies.

@@

The UV Index computed from satellite-based observations
over the period 2005-2019 is shown in
Figure~{\ref{485116}}. The satellite-derived UVIs vary
from 8 in winter to 16 in summer, these values being substantially higher
than the ground-based observations (ca. 7 for winter and 11 for summer,
see Fig.~{\ref{310112}}). For both datasets the maximum values
are reached in June and July of each year. We hypothesize that this
large difference between satellite-based estimation and ground-based
observation of the UV index is due to the intense air pollution of
Mexico City.~A rather similar behavior was detected in Santiago city,
Chile.\citep{Cabrera_2012} Although the OMI data are corrected for climatological aerosol absorption\citep{Arola_2009}, this correction likely underestimates the absorption within the polluted Mexico City BL.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{Conditions for estimation in June-July} & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    \begin{tabular}[c]{@{}l@{}}OMI maximum value reached in period 2005-2019,\\ not corrected for BL aerosols\end{tabular}                      & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV pristine pollution\\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{UVI maxima for June-July: averages and standard deviation from ground-based data
        for the years 2018-2019 and 2000-2001. UVI maximum value reached in the period 2000-2019 for
        UVI ground-based and the same for satellite in the period 2005-2019. TUV calculations for different conditions.
      }}
  \label{table:TUVmodel}
\end{table}

@@

Table~{\ref{table:year2000-2019}} shows the
contributions to UVI reductions from individual pollutants. Aerosols are
seen to be the major factor in both time periods, followed by
O\textsubscript{3}, NO\textsubscript{2}, and SO\textsubscript{2}. The
2000-2019 UVI increase results in comparable proportions from
less aerosols, less SO\textsubscript{2}, and the combined reductions in
O\textsubscript{3} and NO\textsubscript{2}.

Comparable UV reductions, of 30-40\% due to aerosols, were reported by
\citet{Panicker_2009} over Pune, India from April 2004 to
March 2005, with sensitivity coefficients (i.e. change in UVI per unit
change in AOD) similar to those found here in Table~\ref{table:TUVmodel}.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lccccc}
    \hline
    \multicolumn{1}{c}{\multirow{2}{*}{Pollutant}} & \multicolumn{2}{c}{Year 2000} & \multicolumn{2}{c}{Year 2019} & 2000-2019                 \\ \cline{2-6}
    \multicolumn{1}{c}{}                           & poll. level (a)               & UVI (b)                       & poll. level & UVI   & (c) \\ \hline
    AOD                                            & 0.7                           & -3.7                          & 0.5         & -2.7  & 1.0 \\
    O\textsubscript{3} ppb (DU)                    & 70 (14)                       & -1.4                          & 50 (10)     & -1.0  & 0.4 \\
    NO\textsubscript{2} ppb                        & 40                            & -0.9                          & 20          & -0.5  & 0.4 \\
    SO\textsubscript{2} ppb                        & 30                            & -0.8                          & 1           & -0.04 & 0.8 \\ \hline
  \end{tabular}
  \caption{Contributions of individual pollutants to UV Index changes. (a) Values used one at the time, with the others held at zero. (b) UVI deviation from the zero-pollution value of 16.1 (from Table \ref{table:TUVmodel}). (c) 2000-2019 UVI change due to changes in each pollutant.}
  \label{table:year2000-2019}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Place any additional packages needed here.  Only include packages
%% which are essential, to avoid problems later.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{chemformula} % Formula subscripts using \ch{}
\usepackage[T1]{fontenc} % Use modern font encodings
\usepackage{lineno}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{multirow}

@@

The question of how air pollution alters the urban UV environment
(and~\emph{vice versa}) is not new, but studies have relied mostly on
numerical models \cite{Liu_1991,Sabziparvar_1998,Madronich_2011},
with relatively few available observations (e.g.,
\citet{McKenzie_2008}, \citet{Panicker_2009}, \citet{Palancar_2013},
reviewed by \citet{Bais_2015}). Increases in UV have been estimated as a consequence
of emission reductions over the last decades, e.g. in China,\citep{Hollaway_2019,Li_2018,Wang_2020}
and have led to less-than-expected
reductions in photochemical smog, in part due to stronger UV
photochemistry.\citep{Wang_2019,Gao_2020,Ma_2021}
Emission reductions have also occurred
globally during the 2020 COVID-19 pandemic,\citep{Bauwens_2020,Venter_2020}
but ground-level ozone in some polluted areas has actually
increased,\citep{Shi_2020,Le_2020} due at least in part to the increased UV
radiation. Unfortunately, the observational data base of relevant UV
radiation remains rather sparse to evaluate such model-predicted feedbacks between chemistry and radiation.~~

@@

The UVI is recognized by the World Health and Meteorological
Organizations (WHO and WMO) as a standardized measure of UV
radiation\cite{who2002} for global public information. An advantage
of using the UVI as (one) measure of UV radiation is that it is being
increasingly observed or calculated and disseminated, enabling more
objective comparisons among seasons and locations. The UVI observations
from Mexico City, considered here, are an important element of this
global picture.

@@

The UV Index data derived from satellite-based measurements
were used for comparison with the ground-based measurements.
These data were provided by the Ozone Monitoring
Instrument (OMI)~on board of AURA-NASA satellite.\citep{dcio} OMI
is operated in cooperation between the Netherlands Agency for Aerospace
Programmes (NIVR), the Finnish Meteorological Institute (FMI) and NASA.
OMI performs observations over a geographical area of 13$\times$24km\textsuperscript{2} at nadir. For
the coordinates (19.33°N, 99.18°W) and elevation (2268 m asl) of Mexico City,
the satellite overpass time is between 19:00h - 21:00h UTC (20:00h - 22:00h CET).
The OMI instrument measures reflected and backscattered radiances of the atmosphere-surface system at several UV wavelengths. The ozone column is estimated by differential absorption of several adjacent
wavelengths in the O\textsubscript{3} Huggins band\citep{Veefkind_2006}, while clouds are estimated from the reflectivity at a wavelength not affected by O\textsubscript{3} absorption (360 nm, \citet{Tanskanen_2007}). A correction for absorbing aerosols is made using a global aerosol climatology.\citep{Arola_2009}
The UV Index used for Mexico City corresponds to values at local noon time and clear sky
from OMUVB Level 2 OVP data product, version 1.3 and collection 3.

@@

Above the atmospheric boundary layer, the model atmosphere was specified to be,
NO\textsubscript{2}, or SO\textsubscript{2}. In one
sensitivity study, a total AOD of 0.7 was redistributed placing 0.2 in
the free troposphere (decreasing vertically with an exponential scale
height of 4 km, and 0.5 remaining in the BL). The calculated UVI
differed by less than 1\%. Thus, as long as the total AOD is known,
knowledge of the exact vertical aerosol profile is not critical for
ground-level UVI, but would obviously affect the vertical structure of
photolysis frequencies.

@@

The UV Index computed from satellite-based observations
over the period 2005-2019 is shown in
Figure~{\ref{485116}}. The satellite-derived UVIs vary
from 8 in winter to 16 in summer, these values being substantially higher
than the ground-based observations (ca. 7 for winter and 11 for summer,
see Fig.~{\ref{310112}}). The maximum values are reached in June and July of each year for both data sets.
We hypothesize that this large difference between satellite-based estimation and ground-based
observation of the UV index is due to the intense air pollution of
Mexico City.~A rather similar behavior was detected in Santiago city,
Chile.\citep{Cabrera_2012} Although the OMI data are corrected for climatological aerosol absorption\citep{Arola_2009}, this correction likely underestimates the absorption within the polluted Mexico City BL.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{Conditions for estimation in June-July} & \textbf{UV Index} \\ \hline
    SIMAT average maxima 2000-2001                  & 9.9  $\pm$  1.2   \\ \hline
    SIMAT average maxima 2018-2019                  & 12.3 $\pm$  1.3   \\ \hline
    SIMAT maximum value reached in period 2000-2019 & 15.0              \\ \hline
    OMI maximum value reached in period 2005-2019   & 16.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV "zero" pollution \\ AOD 0, O\textsubscript{3} 0 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 16.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}
      }TUV pristine pollution \\ AOD 0.05, O\textsubscript{3} 10 ppb, NO\textsubscript{2} 0 ppb, SO\textsubscript{2} 0 ppb\end{tabular}                      & 15.6              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2019:\\ AOD 0.5, O\textsubscript{3} 50 ppb, NO\textsubscript{2} 20 ppb, SO\textsubscript{2} 1 ppb\end{tabular}                      & 12.1              \\ \hline
    \begin{tabular}[c]{@{}l@{}}TUV 2000:\\ AOD 0.7, O\textsubscript{3} 70 ppb, NO\textsubscript{2} 40 ppb, SO\textsubscript{2} 20 ppb\end{tabular}                      & 10.2              \\ \hline
  \end{tabular}
  \caption{{UVI maxima for June-July: averages and standard deviation from ground-based data
        for the years 2018-2019 and 2000-2001. UVI maximum value reached in the period 2000-2019 for
        UVI ground-based and the same for satellite in the period 2005-2019. TUV calculations for specified conditions.
      }}
  \label{table:TUVmodel}
\end{table}

@@

Table~{\ref{table:year2000-2019}} shows the contribution of different pollutants
to the UVI increase between 2000 and 2019, computed with the TUV model.
The year 2000 was taken as the base case, and each pollutant was decreased
to its 2019 value individually while the others were maintained at their 2000 value.
Decreasing aerosol AOD has been the largest driver of the UVI changes,
but the absorption by gaseous pollutants has also decreased significantly.
Additional future reductions in AOD, NO\textsubscript{2}, and O\textsubscript{3} could increase the
UVI further, while the low SO\textsubscript{2} levels reached by 2019 are expected
to have negligible effects in the UVI.

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{figures/Monthly_mean_RD.png}
  \caption{The percentage relative difference (\% RD) of the satellite and ground-based monthly means UVI for the period 2005-2019.}
  \label{fig:percentage_relative_difference}
\end{figure}

Figure \ref{fig:percentage_relative_difference} shows the percentage relative difference between monthly means
satellite-based and ground-based data with respect to the last one. The mean percentage relative difference
was 35\% in the period 2005-2019. Comparable UV reductions, of 30-40\% due to aerosols, were reported by
\citet{Panicker_2009} over Pune, India from April 2004 to
March 2005, with sensitivity coefficients (i.e. change in UVI per unit
change in AOD) similar to those found here in Table~\ref{table:TUVmodel}.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{cc}
    \hline
    Pollutant & UVI Change\\ \hline
    AOD & 0.8\\
    O\textsubscript{3} & 0.4\\
    NO\textsubscript{2} & 0.4\\ 
    SO\textsubscript{2} & 0.5 \\ \hline
  \end{tabular}
  \caption{Contributions of individual pollutants to the 2000-2019 UV Index changes. Baseline calculation for 2000 conditions (AOD = 0.7, O\textsubscript{3} = 70 ppb, NO\textsubscript{2} = 40 ppb, SO\textsubscript{2} = 20 ppb). Individual pollutant contributions are estimated by adjusting each pollutant, one at the time, to its 2019 value (AOD = 0.5, O\textsubscript{3} = 50 ppb, NO\textsubscript{2} = 20 ppb, SO\textsubscript{2} = 1 ppb), while maintaining the others at their 2000 value.}
  \label{table:year2000-2019}
\end{table}
